Data Exploration

### 2018-11-13 src/data_exploration.Rmd
packrat update

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
```{r pre-install packages, message=FALSE}
packages <- c() 
source("../src/ipak.R")
ipak(packages)
```

@@

>>>>

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
The "include=FALSE" supresses the package installation text appearing in the document...
```{r pre-install packages, include=FALSE}
packages <- c("plyr") 
source("../src/ipak.R")
ipak(packages)
```

@@

# Update: Observations by Cell (in total and by time-step)

as the title says... how many observations happeend in each cell:
- in total

```{r observation by cell - total}
library(plyr) #to use the count function
obs_by_cell <- count(presence, "cell_id")
write.csv(obs_by_cell, file = "../output/bio/no_observations_cell.csv")
head(obs_by_cell)
```

- in each yyyymm
```{r}
obs_cell_yymm <- count(presence, c("cell_id", "year", "month"))
write.csv(obs_cell_yymm, file = "../output/bio/no_observations_cell_yymm.csv")
head(obs_cell_yymm)
```
